Technical Report

### 2017-10-23 fully-abstract-comp/technical-report.tex
reformatting

\section{Logical Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\lau{19-10-2017: Maybe linearity should be taken care of in just one place (instead of in $\lrr$ relation and mem staisfaction). That is, add a predicate that checks whether the configuration satisfies linearity (such a condition may be to syntactic to work?).}
\[
  \lre(W) = \left\{ \npair{\stpair{v}{v}} \middle| 
    \begin{array}{l}
      \forall n' \leq n \ldotp \\
      \quad \forall \npair[n']{\stpair[.]{(k_{d,S},k_{c,S})}{(k_{d,T},k_{c,T})}} \in \lrk(W) \ldotp \\
      \qquad \forall \stpair{\reg}{\reg}\ldotp \npair[n']{
      \left(\array{l}\src{\reg_S\updReg{\pcreg,\rretd,\rretc}{v_S,k_{d,S},k_{c,S}}},\\\reg_T\updReg{\pcreg,\rretd,\rretc}{v_T,k_{d,T},k_{c,T}}\endarray\right)} \in \lrr(W) \Rightarrow\\
      \qquad \quad \forall \src{\ms_S},\ms_T \ldotp \memSat[n']{\stpair[.]{\ms}{\ms}}{\stpair{\reg}{\reg}}{W} \Rightarrow \\
      \qquad \qquad \npair[n']{\left(\array{l}\src{(\reg_S\updReg{\pcreg}{v_S}\updReg{r_\ret}{k_V},\ms_S)},\\(\reg_T\updReg{\pcreg}{v_T}\updReg{r_\ret}{k_T},\ms_T)\endarray\right)}
      \in \lro(W)
    \end{array}
            \right\}
\]

\[
  \lro(W) = \left\{ \npair{\stpair[.]{(\reg_S,\ms_S,\stk_S,\ms_{\stk,S})}{\reg_R,\ms_R}} \middle|
    \begin{array}{l}
      \forall i \leq n, \stpair{\mem}{\mem} \ldotp \\
      \quad \src{(\reg_S,\ms_S \cup \mem_S,\stk_S,\ms_{\stk,S})} \term[i] \Rightarrow (\reg_R,\ms_R) \term\\
      \quad tand\\
      \quad (\reg_R,\ms_R) \term[i] \Rightarrow \src{(\reg_S,\ms_S \cup \mem_S,\stk_S,\ms_{\stk,S})} \term
    \end{array}
\right\}
\]

@@

\[
  \lrr(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : \RegName \fun \World \ldotp \\
      \quad S \text{ is a separation of $W$} \tand
      \quad \forall r \in \dom(\reg_T) \setminus \{\pcreg, \rretd,\rretc \}\ldotp
      \npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
Where $S\text{ is a separation of $W$}$ means that no two partion share the same ``pure'' region (whatever that is).

>>>>

\section{Logical Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\lau{19-10-2017: Maybe linearity should be taken care of in just one place (instead of in $\lrr$ relation and mem staisfaction). That is, add a predicate that checks whether the configuration satisfies linearity (such a condition may be to syntactic to work?).}
In the following definitions, \src{blue} is used to indicate values related to the source machine. This is unlike previous definitions, where \src{blue} is used  indicate source language specific parts of definitions.
\[
  \lre(W) = \left\{ \npair{\stpair{v}{v}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{k_{d,S}}, \src{k_{c,S}}, k_{d,T}, k_{c,T}, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad\src{\reg_S}(\rretd,\rretc,\pcreg) = \src{k_{d,S}}, \src{k_{c,S}}, \src{v_S} \wedge\\
      \quad\reg_T(\rretd,\rretc,\pcreg) = k_{d,S}, k_{c,S}, v_T \wedge\\
      \quad\npair[n']{\stpair[.]{(k_{d,S},k_{c,S})}{(k_{d,T},k_{c,T})}} \in \lrk(W) \wedge \\
      \quad\stpair{\reg}{\reg}\ldotp \npair[n']{
      \quad\left(\array{l}\src{\reg_S\updReg{\pcreg,\rretd,\rretc}{v_S,k_{d,S},k_{c,S}}},\\\reg_T\updReg{\pcreg,\rretd,\rretc}{v_T,k_{d,T},k_{c,T}}\endarray\right)} \in \lrr(W) \wedge\\
      \quad\src{\ms_S},\ms_T \ldotp \memSat[n']{\stpair[.]{\ms}{\ms}}{\stpair{\reg}{\reg}}{W} \\
      \quad\Rightarrow\\
      \quad\npair[n']{\left(\array{l}\src{(\reg_S\updReg{\pcreg}{v_S}\updReg{r_\ret}{k_V},\ms_S)},\\(\reg_T\updReg{\pcreg}{v_T}\updReg{r_\ret}{k_T},\ms_T)\endarray\right)}
      \in \lro(W)
    \end{array}
            \right\}
\]

\[
  \lro(W) = \left\{ \npair{\stpair[.]{(\reg_S,\ms_S,\stk_S,\ms_{\stk,S})}{\reg_R,\ms_R}} \middle|
    \begin{array}{l}
      \forall i \leq n, \stpair{\mem}{\mem} \ldotp \\
      \quad \src{(\reg_S,\ms_S \cup \mem_S,\stk_S,\ms_{\stk,S})} \term[i] \Rightarrow (\reg_R,\ms_R) \term\\
      \quad \tand\\
      \quad (\reg_R,\ms_R) \term[i] \Rightarrow \src{(\reg_S,\ms_S \cup \mem_S,\stk_S,\ms_{\stk,S})} \term
    \end{array}
\right\}
\]

@@

\[
  \lrr(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : \RegName \fun \World \ldotp \\
      \quad S \text{ is a separation of $W$} \tand\\
      \quad \forall r \in \dom(\reg_T) \setminus \{\pcreg, \rretd,\rretc \}\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
Where $S\text{ is a separation of $W$}$ means that no two partion share the same ``pure'' region (whatever that is).
